Toward theories of deliberated preferences

### 2020-11-03 simple.tex
Totalitarism vocabulary

A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective and surjective binary relation over $\alldargs × \gbeatsinv(\allargs)$. \commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ? pourquoi ? à quoi est-ce que cela sert ?} 
These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton. 
Note that $\dbeats$ need not be a bijection as it is generally not a function. 
Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie. Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}

>>>>

A defense relation ${\dbeats} \subseteq \alldargs × \gbeatsinv(\allargs)$ is an injective (left-unique) and surjective (right-total) binary relation over $\alldargs × \gbeatsinv(\allargs)$. \commentYM{le fait qu'elle soit surjective et injective est une exigence que tu poses dans la définiton ? pourquoi ? à quoi est-ce que cela sert ?} 
These constraints guarantee that every anticipated attack has exactly one fragment defending against it, thus, $\forall \ar_1 \suchthat [\exists \ar_0 \suchthat \ar_1 \gbeats \ar_0]$: $\dbeatsinv(\ar_1)$ is a singleton. 
Note that $\dbeats$ need not be a bijection as it is generally not a function (it is not restrictive to suppose it left-total, but it is generally not right-unique). 
Given $\ar_1 \in \gbeatsinv(\allargs)$, define $\dbeatsinv(\ar_1)$ as the fragment defending against the anticipated attack $\ar_1$.
\commentYM{dans toute cette sous-section la lecture est rendue très difficile par ce genre de formulation qui assigne une intentionnalité à la théorie. Je ne comprends pas le sens métaphorique de ces phrase, donc je ne les comprends pas}
